Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-08-23 manuscript/draft.Rmd
clarify fig 3 text
some added clarification to remind readers. this also isn't the strict definition of forecast horison.

![Performance of the six models we evaluated when predicting one year into the
future (2004) or ten years into the future (2013).  In general, the single-site
models (**A.**) outperformed the environmental models. (**B.**) The accuracy of
the predictions generally declined as the forecast horizon was
extended.](../figures/scatter.png)

>>>>

![Performance of the six models, trained with data from 1982-2003, when 
predicting one year into the future (2004) or ten years into the future (2013).
In general, the single-site models (**A.**) outperformed the environmental
models (**B.**). The accuracy of the predictions generally declined as the
timescale of the forecast was extended from 2004 to 2013.](../figures/scatter.png)
